paper

### 2022-04-01 outputs/paper.Rmd
small changes in graph for figure 5 &6

# plot bar graph for caretaker comparisons and administrative regions
child %>% 
  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity') + 
  labs(x = "caretaking preference",
       y = "percentage",
       fill = "Administrative regions") +
  theme_minimal() +
  coord_flip() +
  facet_wrap(~background) +
  theme(legend.position = "bottom")

@@

```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
# looking at the number of employed women selected in the different administrative regions
# with the child under six
child %>% 
  filter(x == "no child under six" | x == "one or more child under six") %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity') +
  labs(x = "child status",
       y = "percentage",
       fill = "region") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip() +
  facet_wrap(~background)

>>>>

# plot bar graph for caretaker comparisons and administrative regions
child %>% 
  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity') + 
  labs(x = "caretaking preference",
       y = "percentage") +
  theme_minimal() +
  coord_flip() +
  facet_wrap(~background) +
  theme(legend.position = "none")

@@

```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
# looking at the number of employed women selected in the different administrative regions
# with the child under six
child %>% 
  filter(x == "no child under six" | x == "one or more child under six") %>% 
  ggplot(aes(x = background,
             y = percentage,
             fill = x)) +
  geom_bar(stat = 'identity', position = "dodge", width = 0.8) +
  labs(x = "child status",
       y = "percentage",
       fill = "child status") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
